Active Learning for SAT Solver Benchmarking

### 2023-01-24 paper/paper.tex
minor

The Wilcoxon stopping criterion stops the active-learning process when we are confident enough that the predicted runtime labels of the new solver are sufficiently different from existing solvers.
This criterion is loosely inspired by Matricon et.~al.~\cite{MatriconAFSH21}.
We use the average $p$-value $W_{\hat{a}}$ of a Wilcoxon signed-rank test $w(S,P)$ of the two runtime label distributions $S=\{ \gamma(a, e) \mid e \in \mathcal{I} \}$ for an existing solver $a$ and \mbox{$P=\{ f(\hat a, e) \mid e \in \mathcal{I} \}$} for the new solver $\hat{a}$:
%
\begin{equation*}
  W_{\hat{a}} := \frac{1}{\lvert \mathcal{A} \rvert} \sum_{a \in \mathcal{A}} \operatorname{w}(S, P)
\end{equation*}
%
To improve the stability of this criterion, we use an exponential moving average to smooth out outliers and stop as soon as $W^{(i)}_{\exp}$ drops below a fixed threshold:
%
\begin{align*}
  W_{\exp}^{\left(0\right)} &:= 1\\
  W_{\exp}^{\left(i\right)} &:= \beta W_{\hat{a}} + \left(1 - \beta\right) W_{\exp}^{\left(i - 1\right)}
\end{align*}

>>>>

The Wilcoxon stopping criterion stops the active-learning process when we are confident enough that the predicted runtime labels of the new solver are sufficiently different from existing solvers.
This criterion is loosely inspired by Matricon et.~al.~\cite{MatriconAFSH21}.
We use the average $p$-value $W_{\hat{a}}$ of a Wilcoxon signed-rank test $\operatorname{w}(S,P)$ of the two runtime label distributions $S=\{ \gamma(a, e) \mid e \in \mathcal{I} \}$ for an existing solver $a$ and \mbox{$P=\{ f(\hat a, e) \mid e \in \mathcal{I} \}$} for the new solver $\hat{a}$:
%
\begin{equation*}
  W_{\hat{a}} := \frac{1}{\lvert \mathcal{A} \rvert} \sum_{a \in \mathcal{A}} \operatorname{w}(S, P)
\end{equation*}
%
To improve the stability of this criterion, we use an exponential moving average to smooth out outliers and stop as soon as $W^{(i)}_{\exp}$ drops below a fixed threshold:
%
\begin{align*}
  W_{\exp}^{\left(0\right)} &:= 1\\
  W_{\exp}^{\left(i\right)} &:= \beta W_{\hat{a}} + \left(1 - \beta\right) W_{\exp}^{\left(i - 1\right)}
\end{align*}
